A Domain Specific Language for SpectreGuard

### 2020-12-09 paper/main.tex
Introduction

% \addtolength{\jot}{3mm}

@@

\section{Introduction}
Introduction goes here.

@@

\section{Syntax}
A correspondence between the syntax of the EDSL, which is inherited from
Haskell, and the C language is given in Fig. \ref{fig:Syntax}. In the right column, an
overline indicates that the transformation from EDSL to C is recursively
performed to the expression or command underneath the overline.

@@

% \begin{figure}
% \begin{lstlisting}[language=Haskell]
% analyze(forest, scope, return x) = forest
% analyze(forest, scope, (do { n <- allocPublic @ty size; r n })) = do
%   scope.insert(Public, n)
%   analyze(forest, scope, r(n))

% analyze(forest, scope, (do { n <- allocSecret @ty size; r n })) = do
%   scope.insert(Secret, n)
%   analyze(forest, scope, r(n))

% analyze(forest, scope, (do { n <- decl x; r n })) = do
%   scope.insert(Public, n)
%   analyze(forest, scope, r(n))

% analyze(forest, scope, (do { x .= y; r })) = do
%   let lhsNames = collectExprNames(x)
%   let rhsNames = collectExprNames(y)

%   foreach rhsName in rhsNames
%     if (rhsName is secret)
%       forest.addChildrenTo(rhsName, lhsNames)
%     end
%   end

%   foreach lhsName in lhsNames
%     let scopeFrame = scope.getScopeFrameOf(lhsName)

%     if scope.notCurrentScopeFrame(scopeFrame)
%       forest.addChildrenTo(lhsName, scopeFrame.secretVariables)
%     end
%   end

%   analyze(forest, scope, r)

% analyze(forest, scope, (do { ifThenElse cond t f; r })) = do
%   let secretNames = filter(isSecretName, collectExprNames(cond))

%   let tForest = copy(forest)
%   let fForest = copy(forest)
%   let tScope = copy(scope)
%   let fScope = copy(scope)

%   analyze(tForest, tScope.pushFrame(secretNames), r)
%   analyze(fForest, fScope.pushFrame(secretNames), r)

%   forest = union(tForest, fForest)
%   analyze(forest, scope, r)
% \end{lstlisting}
% \caption{Information leak analysis pseudocode}
% \end{figure}

% \begin{figure}[h]
%   \centering
% \resizebox{0.68\linewidth}{!}{
% \begin{minipage}{\linewidth}
%   \centering
% \begin{gather*}
%   \inference{%
%     \Delta;\Gamma \vdash \ttt{x :: $\tau$}
%     \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
%     \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
%     }
%     {%
%       \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
%     }\\
%     \\
%   \inference{%
%     \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
%     & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
%     \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
%     & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
%     \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
%     }
%     {%
%       \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
%     }\\
%   \\
%   \inference{%
%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
%     & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
%     \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
%     }
%     {%
%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
%     }\\
%   \\
%   \inference{%
%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
%     \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
%     & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
%     \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
%     }
%     {%
%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
%     }\\
%   \\
%   \inference{%
%     \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
%     \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
%     & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
%     \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
%     & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
%     \\ \Delta;\Gamma \vdash Pub(\ttt{x})
%     }
%     {%
%       \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
%     }\\
%   \\
%   \inference{%
%     \Delta;\Gamma \vdash v \in L(\ttt{x})
%     }
%     {%
%       \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
%     }
% \end{gather*}
% \end{minipage}}
%   \caption{Information flow analysis rules which define the relation $\sarr$}
% \label{fig:FlowRules}
% \end{figure}
...

% \section{Your System}
% ...
% \section{Evaluation}
% ...

>>>>

@@

\section{Introduction}
SpectreGuard is provides an abstraction that allows programmers to prevent
speculative access of certain variables.~\cite{SpectreGuard} For
preserving program correctness, static analyses are desirable to prevent
programmers from accidentally successfully compiling code which copies a
``secret'' variable (a variable protected by SpectreGuard) to a ``public''
variable (a variable with no such protection).

To this end, two interrelated static analysis techniques are designed and
implemented. In this paper, we make the following contributions:

\begin{itemize}
\item We describe a small domain specific language embedded in Haskell for representing
  simple C programs (Section~\ref{sec:Syntax}).
\item A code generator which generates C code from this EDSL is outlined
  (Section~\ref{sec:Syntax}).
\item We give a system of types which causes the expression language of this
  EDSL to be statically checked for variable copies that directly leak memory
  from secret variables to public variables (Section~\ref{sec:SensTypes}).
\item Another static analysis procedure is given which can find \textit{indirect}
  leak paths through control structures (Section~\ref{sec:Analysis}). This analysis
  procedure can be applied to EDSL code in the same way as the code generator
  can be applied to EDSL code. The results from this analysis take the form
  of a forest of multiway trees, providing information about these possible
  indirect leaks.
\end{itemize}

@@

\section{Syntax}
\label{sec:Syntax}
A correspondence between the syntax of the EDSL, which is inherited from
Haskell, and the C language is given in Fig. \ref{fig:Syntax}. In the right column, an
overline indicates that the transformation from EDSL to C is recursively
performed to the expression or command underneath the overline.

@@
